Refinements for open automata

### 2021-07-30 2021-Refinement/paper/refinementarticle.tex
just drafting the contributions

>>>>

Contributions:

We first: introduce open automata (NOT NEW), their composition, and the deadlock-free composition.

Then we define a refinement relation for open automata that has the following characteristics:

- good behaviour wrt composition

- refinement does not introduce deadlock

- a first relation that focuses on the automaton part and a second that deals partially with open behaviour

we will see that having at the same time composition and transitivity also raises challenges; we introduce a relation that addresses this challenge.
